---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE, message = FALSE}
devtools::load_all()
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# predictr

[![Travis-CI Build Status](https://travis-ci.org/craiggrabowski/predictr.svg?branch=master)](https://travis-ci.org/craiggrabowski/predictr)
[![codecov](https://codecov.io/gh/craiggrabowski/predictr/branch/master/graph/badge.svg)](https://codecov.io/gh/craiggrabowski/predictr)
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/craiggrabowski/predictr?branch=master&svg=true)](https://ci.appveyor.com/project/craiggrabowski/predictr)

The goal of predictr is to allow for model predictions which 
minimize memory usage and computing time.
This package provides a new type of object and adaptors for
various common model types.


## Installation

You can install predictr from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("craiggrabowski/predictr")
```

## Example

This is a basic example which illustrates the main method:

```{r example}
## basic example code
v <- seq(1024)
df <- data.frame(x = v, y = v + 1)
model <- lm(y ~ x, df)
x <- predictor(model)
predict(x, data.frame(x = c(2, 3)))
```

In this example,
we call predictor on a model object produced using linear
regression.
This new object implements the predict method,
except now the output is expressed as a matrix.
There are a few reasons for performing this extra step.
First,
the new object is significantly smaller than the existing model
object:

```{r}
pryr::object_size(model)
pryr::object_size(x)
```

Second,
the predict method is now faster for large data:
```{r}
a <- data.frame(x = seq(100000))
microbenchmark::microbenchmark(predict(model, a), predict(x, a))
```

Third,
the new object converts to a predict function which is even faster:
```{r}
f <- as.function(x)
microbenchmark::microbenchmark(predict(x, a), f(a))
```
